---
title: "Regression analysis - winequality data- group 33"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## import data from csv file and make pairs plot for the data
```{r}
redwine <- read.csv(file="winequality-red.csv", sep=";")
whitewine <- read.csv(file="winequality-white.csv", sep=";")

pairs(dataset, main="red wine")
pairs(dataset, main="white wine")

```
## Loading libraries 
```{r}
install.packages("corrplot")
install.packages("Hmisc")
install.packages("MPV")
install.packages("faraway")
library(corrplot)
library(Hmisc)
library(MPV)
library(faraway)
str(dataset)

```


##Introducing a new data point to our data

```{r}
red <- rbind(dataset,c(8.32,0.5278,0.271,2.539,0.0874,15.87,46.47,0.9967,3.311,0.6581,10.42,6))
str(red)
white <- rbind(dataset,c(0.528,0.2471,2.77,8.21,0.9967,3.311,0.6581,0.0874,15.87,46.47,132,6.11))
str(white)

```

## take summary of the data.

```{r}
summary(red[,1:11])
summary(white[,1:11])

```


##make Box-Plot for all the independent variables for red wine by quanlity.

```{r pressure, echo=FALSE}
boxplot(volatile.acidity~quality, data= red)
boxplot(chlorides~quality, data= red)
boxplot(free.sulfur.dioxide~quality, data= red)
boxplot(total.sulfur.dioxide~quality, data= red)
boxplot(sulphates~quality, data= red)
boxplot(alcohol~quality, data= red)

```
##Box-Plot for white wine

```{r pressure, echo=FALSE}
boxplot(volatile.acidity~quality, data= white)
boxplot(chlorides~quality, data= white)
boxplot(free.sulfur.dioxide~quality, data= white)
boxplot(total.sulfur.dioxide~quality, data= white)
boxplot(sulphates~quality, data= white)
boxplot(alcohol~quality, data= white)

```

## Correlation Matrix 

```{r}
res <- rcorr(as.matrix(dataset[,1:11]))
res$P

corrplot( res$r, type="upper", p.mat=res$p, sig.level=0.01)

```


##Fi a linear regression on all the variables for red wine and take vif score
```{r}
lm1 <- lm( quality~fixed.acidity+volatile.acidity+citric.acid+residual.sugar+chlorides+free.sulfur.dioxide+total.sulfur.dioxide+density+pH+sulphates+alcohol, data= red)
summary(lm1)
vif(lm1)
plot(lm1)
```


#Fit the linear regression model based on the significant variables for red wine.

```{r}
lm2 <- lm( quality~volatile.acidity+chlorides+free.sulfur.dioxide+total.sulfur.dioxide +pH+sulphates+alcohol, data= red)
summary(lm2)
vif(lm2)

plot(lm2)
```

```{r}
vif(lm1,lm2)
```

##Fit a linear regression on all the variables for white wine
```{r}
lm11 <- lm( quality~fixed.acidity+volatile.acidity+citric.acid+residual.sugar+chlorides+free.sulfur.dioxide+total.sulfur.dioxide+density+pH+sulphates+alcohol, data= white)
summary(lm11)
vif(lm11)
plot(lm11)
```


##Fit the linear regression model based on the significant variables for white wine.

```{r}
lm2 <- lm( quality~volatile.acidity+chlorides+free.sulfur.dioxide+total.sulfur.dioxide +pH+sulphates+alcohol, data= white)
summary(lm22)
vif(lm22)
plot(lm22)
```

```{r}
vif(lm11,lm22)
```
